---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lazyseurat

<!-- badges: start -->
<!-- badges: end -->

The goal of lazyseurat is to allow import and export Seurat objects to and from
    file-backed storage. 
    Note that LazySeurat is not meant to be used during analysis, 
    but rather for data visualisation on research dissemination
    platforms, where it can save computational costs.

## Installation

You can install the development version of lazyseurat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jeskowagner/LazySeurat")
```

## Example

Convert a Seurat object to allow lazy loading:

```{r export_seurat}
library(lazyseurat)
library(SeuratData)
# Get example data
InstallData("pbmc3k")
data("pbmc3k")

# Export Seurat object to feather for lazy loading
write_seurat_to_feather("lazyseurat")
```

